---
title: "Japanese & Korean politeness: Perception"
author: "Bodo Winter, Kaori Idemaru"
date: "9/17/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preprocessing

This is new production data on Japanese. We begin by loading the required packages:

```{r load_packages, message = FALSE}
library(lme4) # for mixed models
library(afex) # for likelihood ratio tests
library(tidyverse) # for data processing
library(stringr) # for data processing
```

Let's load in the Japanese productin data:

```{r load_data, message = FALSE}
# Load:

jprod <- read_csv('../data/JPNpolitenessProduction.csv')

# Stats:

nrow(jprod)

ncol(jprod)

# Show:

jprod %>% print(n = 2, width = Inf)
```

Add unique item identifiers by pasting task and scenario together (scenario numbers 1:6 are repeated across tasks):

```{r unique_item_IDs}
jprod <- mutate(jprod,
                item = str_c(langtask, ':', scenario))
```

Since there will be interactions, let's deiviation-code the categorical predictors that will feature in interactions:

```{r add_contrast_cdes}
jprod <- mutate(jprod,
                condition2_c = ifelse(condition2 == 'polite', 0.5, -0.5),
                gender_c = ifelse(gender == 'M', 0.5, -0.5),
                task_c = ifelse(task == 'epr', -0.5, 0.5))
```

Log-transform the duration measure:

```{r log_durations}
jprod <- mutate(jprod,
                duroriginal = dur,
                dur = log10(dur))
```

## Descriptive statistics (for each acoustic measure)

Descriptive statistics for all measures, means:

```{r descriptive_means}
jprod %>% group_by(condition2) %>% 
  summarize(f0_M = mean(f0mdhz),
            f0sd_M = mean(f0sdhz),
            intmd_M = mean(inmd),
            intsd_M = mean(insd),
            jit_M = mean(jitloc),
            shim_M = mean(shimloc),
            H1H2_M = mean(h1mh2mn),
            HNR_M = mean(mnHNR),
            rate_M = mean(rate)) %>%
  print(width = Inf)
```

Same for SDs:

```{r descriptive_sds}
jprod %>% group_by(condition2) %>% 
  summarize(f0_SD = sd(f0mdhz),
            f0sd_SD = sd(f0sdhz),
            intmd_SD = sd(inmd),
            intsd_SD = sd(insd),
            jit_SD = sd(jitloc),
            shim_SD = sd(shimloc),
            H1H2_SD = sd(h1mh2mn),
            HNR_SD = sd(mnHNR),
            rate_SD = sd(rate)) %>%
  print(width = Inf)
```

For duration, only DCT (since it can have variable length):

```{r dur_descriptive}
jprod %>% filter(task == 'ppt') %>% 
  group_by(condition2) %>% 
  summarize(logdur_M = mean(dur),
            logdur_SD = sd(dur),
            dur_M = mean(duroriginal),
            dur_SD = sd(duroriginal))
```

## Mixed models (for each acoustic measure)

Pitch:

```{r f0_mdl}
j_f0 <- mixed(f0mdhz ~ condition2_c *
                (gender_c + task_c) +
                (1 + condition2_c|speaker) +
                (1 + condition2_c|item),
              data = jprod, method = 'LRT')
j_f0
```

Pitch variability (standard deviations):

```{r f0sd_mdl}
j_f0sd <- mixed(f0sdhz ~ condition2_c *
                (gender_c + task_c) +
                (1 + condition2_c|speaker) +
                (1 + condition2_c|item),
              data = jprod, method = 'LRT')
j_f0sd
```

Intensity:

```{r int_mdl}
j_int <- mixed(inmd ~ condition2_c *
                (gender_c + task_c) +
                (1 + condition2_c|speaker) +
                (1 + condition2_c|item),
              data = jprod, method = 'LRT')
j_int
```

Intensity variability (standard deviation):

```{r int_sd_mdl}
j_intsd <- mixed(insd ~ condition2_c *
                (gender_c + task_c) +
                (1 + condition2_c|speaker) +
                (1 + condition2_c|item),
              data = jprod, method = 'LRT')
j_intsd
```

Jitter:

```{r jitter_mdl}
j_jit <- mixed(jitloc ~ condition2_c *
                (gender_c + task_c) +
                (1 + condition2_c|speaker) +
                (1 + condition2_c|item),
              data = jprod, method = 'LRT')
j_jit
```

Shimmer:

```{r shimmer_mdl}
j_shim <- mixed(shimloc ~ condition2_c *
                (gender_c + task_c) +
                (1 + condition2_c|speaker) +
                (1 + condition2_c|item),
              data = jprod, method = 'LRT')
j_shim
```

H1-H2:

```{r h1h2_mdl}
j_h1h2 <- mixed(h1mh2mn ~ condition2_c *
                (gender_c + task_c) +
                (1 + condition2_c|speaker) +
                (1 + condition2_c|item),
              data = jprod, method = 'LRT')
j_h1h2
```

HNR:

```{r HNR_mdl}
j_HNR <- mixed(mnHNR ~ condition2_c *
                (gender_c + task_c) +
                (1 + condition2_c|speaker) +
                (1 + condition2_c|item),
              data = jprod, method = 'LRT')
j_HNR
```

Rate:

```{r rate_mdl}
j_rate <- mixed(rate ~ condition2_c *
                (gender_c + task_c) +
                (1 + condition2_c|speaker) +
                (1 + condition2_c|item),
              data = jprod, method = 'LRT')
j_rate
```

Duration — just for DCT here since only the discourse completion task has variable length:

```{r dur_DCT_mdl}
j_dur <- mixed(rate ~ condition2_c * gender_c +
                (1 + condition2_c|speaker) +
                (1 + condition2_c|item),
              data = filter(jprod, task == 'ppt'),
              method = 'LRT')
j_dur
```

## Z-scoring Japanese and creating marginal models for plotting:

Z-score all relevant variables:

```{r z_scoring}
jprod_z <- mutate(jprod,
                  f0mnhz = (f0mnhz - mean(f0mnhz, na.rm = T)) / sd(f0mnhz, na.rm = T),
                  f0mdhz = (f0mdhz - mean(f0mdhz, na.rm = T)) / sd(f0mdhz, na.rm = T),
                  f0sdhz = (f0sdhz - mean(f0sdhz, na.rm = T)) / sd(f0sdhz, na.rm = T),
                  f0rghz = (f0rghz - mean(f0rghz, na.rm = T)) / sd(f0rghz, na.rm = T),
                  inmn = (inmn - mean(inmn, na.rm = T)) / sd(inmn, na.rm = T),
                  inmd = (inmd - mean(inmd, na.rm = T)) / sd(inmd, na.rm = T),
                  insd = (insd -mean(insd, na.rm = T)) / sd(insd, na.rm = T),
                  inrange = (inrange - mean(inrange, na.rm = T)) / sd(inrange, na.rm = T),
                  jitloc = (jitloc - mean(jitloc, na.rm = T)) / sd(jitloc, na.rm = T),
                  shimloc = (shimloc - mean(shimloc, na.rm = T)) / sd(shimloc, na.rm = T),
                  h1mh2mn = (h1mh2mn - mean(h1mh2mn, na.rm = T)) / sd(h1mh2mn, na.rm = T),
                  mnHNR = (mnHNR - mean(mnHNR, na.rm = T)) / sd(mnHNR, na.rm = T),
                  dur = (dur - mean(dur, na.rm = T)) / sd(dur, na.rm = T),
                  rate = (rate - mean(rate, na.rm = T)) / sd(rate, na.rm = T))

```

Get subsets of DCT (ppt) and reading task (epr):

```{r ppt_epr_separate}
jprod_ppt <- filter(jprod_z, task == 'ppt')
jprod_epr <- filter(jprod_z, task == 'epr')
```

Create marginal models (no interaction) for plotting:

```{r marginal_models}
# F0:

j_ppt_f0 <- mixed(f0mdhz ~ condition2_c + gender_c + 
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_ppt,
                  method = 'LRT')
j_epr_f0 <- mixed(f0mdhz ~ condition2_c + gender_c +
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_epr,
                  method = 'LRT')

# F0 sd:

j_ppt_f0sd <- mixed(f0sdhz ~ condition2_c + gender_c + 
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_ppt,
                  method = 'LRT')
j_epr_f0sd <- mixed(f0sdhz ~ condition2_c + gender_c +
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_epr,
                  method = 'LRT')

# Intensity:

j_ppt_int <- mixed(inmd ~ condition2_c + gender_c + 
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_ppt,
                  method = 'LRT')
j_epr_int <- mixed(inmd ~ condition2_c + gender_c +
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_epr,
                  method = 'LRT')

# Intensity variability (SD):

j_ppt_intsd <- mixed(insd ~ condition2_c + gender_c + 
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_ppt,
                  method = 'LRT')
j_epr_intsd <- mixed(insd ~ condition2_c + gender_c +
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_epr,
                  method = 'LRT')

# Shimmer:

j_ppt_shim <- mixed(shimloc ~ condition2_c + gender_c + 
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_ppt,
                  method = 'LRT')
j_epr_shim <- mixed(shimloc ~ condition2_c + gender_c +
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_epr,
                  method = 'LRT')

# Jitter:

j_ppt_jit <- mixed(jitloc ~ condition2_c + gender_c + 
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_ppt,
                  method = 'LRT')
j_epr_jit <- mixed(jitloc ~ condition2_c + gender_c +
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_epr,
                  method = 'LRT')

# H1-H2:

j_ppt_h1h2 <- mixed(h1mh2mn ~ condition2_c + gender_c + 
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_ppt,
                  method = 'LRT')
j_epr_h1h2 <- mixed(h1mh2mn ~ condition2_c + gender_c +
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_epr,
                  method = 'LRT')

# HNR:

j_ppt_HNR <- mixed(mnHNR ~ condition2_c + gender_c + 
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_ppt,
                  method = 'LRT')
j_epr_HNR <- mixed(mnHNR ~ condition2_c + gender_c +
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_epr,
                  method = 'LRT')

# Rate:

j_ppt_rate <- mixed(rate ~ condition2_c + gender_c + 
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_ppt,
                  method = 'LRT')
j_epr_rate <- mixed(rate ~ condition2_c + gender_c +
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = jprod_epr,
                  method = 'LRT')

```

## Preprocess Korean data

Load in Korean data:

```{r kor_load}
wg2012 <- read_csv('../data/KRNpolitenessWinterGrawunder2012.csv')
brown2014 <- read_csv('../data/KRNpolitenessProduction_2014.csv')

```

Rename the Korean data for matching acoustic variable names:

```{r kor_rename}
## Process the Korean data:

wg2012 <- wg2012 %>%
  select(language, gender, speaker, task,
         scenario, attitude, dur, rate, f0mnhz,
         f0mdhz, f0sdhz, inmn, inmd, insd, jitloc,
         shimloc, h1mh2mn, mnHNR) %>%
  rename(condition = attitude, item = scenario,
         f0mn = f0mnhz, f0md = f0mdhz, f0sd = f0sdhz)

brown2014 <- brown2014 %>%
  select(language, gender, task,
	       scenario, speaker, condition2,
         dur, rate, f0mnhz, f0mdhz, f0sdhz,
         inmn, inmd, insd, jitloc, shimloc,
         h1mh2mn, mnHNR) %>%
  rename(condition = condition2, item = scenario,
         f0mn = f0mnhz, f0md = f0mdhz, f0sd = f0sdhz)
```

Extract only powerpoint task of Winter & Grawunder (2012) (exclude note task, and newspaper):

```{r extract_dct_kor}
wg2012 <- filter(wg2012, task == 'dct')
```

Log-transform the duration measure for both datasets:

```{r log_durations_kor}
wg2012 <- mutate(wg2012,
                duroriginal = dur,
                dur = log10(dur))
brown2014 <- mutate(brown2014,
                duroriginal = dur,
                dur = log10(dur))
```

Z-score all relevant acoustic variables in both tables:

```{r z_score_allkor}
## Z-score everything, Winter & Grawunder (2012):

wg2012_z <- mutate(wg2012,
                   dur = (dur - mean(dur, na.rm = T)) / sd(dur, na.rm = T),
                   rate = (rate - mean(rate, na.rm = T)) / sd(rate, na.rm = T),
                   inmn = (inmn - mean(inmn, na.rm = T)) / sd(inmn, na.rm = T),
                   inmd = (inmd - mean(inmd, na.rm = T)) / sd(inmd, na.rm = T),
                   insd = (insd - mean(insd, na.rm = T)) / sd(insd, na.rm = T),
                   f0mn = (f0mn - mean(f0mn, na.rm = T)) / sd(f0mn, na.rm = T),
                   f0md = (f0md - mean(f0md, na.rm = T)) / sd(f0md, na.rm = T),
                   f0sd = (f0sd - mean(f0sd, na.rm = T)) / sd(f0sd, na.rm = T),
                   jitloc = (jitloc - mean(jitloc, na.rm = T)) / sd(jitloc, na.rm = T),
                   shimloc = (shimloc - mean(shimloc, na.rm = T)) / sd(shimloc, na.rm = T),
                   h1mh2mn = (h1mh2mn - mean(h1mh2mn, na.rm = T)) / sd(h1mh2mn, na.rm = T),
                   mnHNR = (mnHNR - mean(mnHNR, na.rm = T)) / sd(mnHNR, na.rm = T))

## Z-score everything, Brown et al.(2014):

brown2014_z <- mutate(brown2014,
                      dur = (dur - mean(dur, na.rm = T)) / sd(dur, na.rm = T),
                      rate = (rate - mean(rate, na.rm = T)) / sd(rate, na.rm = T),
                      inmn = (inmn - mean(inmn, na.rm = T)) / sd(inmn, na.rm = T), 
                      inmd = (inmd - mean(inmd, na.rm = T)) / sd(inmd, na.rm = T),
                      insd = (insd - mean(insd, na.rm = T)) / sd(insd, na.rm = T),
                      f0mn = (f0mn - mean(f0mn, na.rm = T)) / sd(f0mn, na.rm = T),
                      f0md = (f0md - mean(f0md, na.rm = T)) / sd(f0md, na.rm = T),
                      f0sd = (f0sd - mean(f0sd, na.rm = T)) / sd(f0sd, na.rm = T),
                      jitloc = (jitloc - mean(jitloc, na.rm = T)) / sd(jitloc, na.rm = T),
                      shimloc = (shimloc - mean(shimloc, na.rm = T)) / sd(shimloc, na.rm = T),
                      h1mh2mn = (h1mh2mn - mean(h1mh2mn, na.rm = T)) / sd(h1mh2mn, na.rm = T),
                      mnHNR = (mnHNR - mean(mnHNR, na.rm = T)) / sd(mnHNR, na.rm = T))
```

To keep everything consistent (even though there are no interactions), make things into deviation coded factors:

```{r kor_fac}
brown2014_z <- mutate(brown2014_z,
                      condition2_c = ifelse(condition == 'polite', 0.5, -0.5),
                      gender_c = ifelse(gender == 'M', 0.5, -0.5))
wg2012_z <- mutate(wg2012_z,
                   condition2_c = ifelse(condition == 'pol', 0.5, -0.5),
                   gender_c = ifelse(gender == 'M', 0.5, -0.5))
```

## Create marginal models for plotting, Korean:

```{r all_marg_models}
## Pitch (median):

k_ppt_f0 <- mixed(f0md ~ condition2_c + gender_c +
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = wg2012_z, method = 'LRT')
k_epr_f0 <- mixed(f0md ~ condition2_c + gender_c +
                    (1 + condition2_c|speaker) +
                    (1 + condition2_c|item),
                  data = brown2014_z, method = 'LRT')

## Pitch variability (sd):

k_ppt_f0sd <- mixed(f0sd ~ condition2_c + gender_c +
                      (1 + condition2_c|speaker) +
                      (1 + condition2_c|item),
                    data = wg2012_z, method = 'LRT')
k_epr_f0sd <- mixed(f0sd ~ condition2_c + gender_c +
                      (1 + condition2_c|speaker) +
                      (1 + condition2_c|item),
                    data = brown2014_z, method = 'LRT')

## Intensity (median):

k_ppt_int <- mixed(inmd ~ condition2_c + gender_c +
                     (1 + condition2_c|speaker) +
                     (1 + condition2_c|item),
                   data = wg2012_z, method = 'LRT')
k_epr_int <- mixed(inmd ~ condition2_c + gender_c +
                     (1 + condition2_c|speaker) +
                     (1 + condition2_c|item),
                   data = brown2014_z, method = 'LRT')

## Intensity variability (sd):

k_ppt_intsd <- mixed(insd ~ condition2_c + gender_c +
                       (1 + condition2_c|speaker) +
                       (1 + condition2_c|item),
                     data = wg2012_z, method = 'LRT')
k_epr_intsd <- mixed(insd ~ condition2_c + gender_c +
                       (1 + condition2_c|speaker) +
                       (1 + condition2_c|item),
                     data = brown2014_z, method = 'LRT')

## Shimmer:

k_ppt_shim <- mixed(shimloc ~ condition2_c + gender_c +
                      (1 + condition2_c|speaker) +
                      (1 + condition2_c|item),
                    data = wg2012_z, method = 'LRT')
k_epr_shim <- mixed(shimloc ~ condition2_c + gender_c +
                      (1 + condition2_c|speaker) +
                      (1 + condition2_c|item),
                    data = brown2014_z, method = 'LRT')

## Jitter:

k_ppt_jit <- mixed(jitloc ~ condition2_c + gender_c +
                      (1 + condition2_c|speaker) +
                      (1 + condition2_c|item),
                    data = wg2012_z, method = 'LRT')
k_epr_jit <- mixed(jitloc ~ condition2_c + gender_c +
                      (1 + condition2_c|speaker) +
                      (1 + condition2_c|item),
                    data = brown2014_z, method = 'LRT')

## H1-H2:

k_ppt_h1h2 <- mixed(h1mh2mn ~ condition2_c + gender_c +
                      (1 + condition2_c|speaker) +
                      (1 + condition2_c|item),
                    data = wg2012_z, method = 'LRT')
k_epr_h1h2 <- mixed(h1mh2mn ~ condition2_c + gender_c +
                      (1 + condition2_c|speaker) +
                      (1 + condition2_c|item),
                    data = brown2014_z, method = 'LRT')

## HNR:

k_ppt_HNR <- mixed(mnHNR ~ condition2_c + gender_c +
                      (1 + condition2_c|speaker) +
                      (1 + condition2_c|item),
                    data = wg2012_z, method = 'LRT')
k_epr_HNR <- mixed(mnHNR ~ condition2_c + gender_c +
                      (1 + condition2_c|speaker) +
                      (1 + condition2_c|item),
                    data = brown2014_z, method = 'LRT')

## Rate:

k_ppt_rate <- mixed(rate ~ condition2_c + gender_c +
                      (1 + condition2_c|speaker) +
                      (1 + condition2_c|item),
                    data = wg2012_z, method = 'LRT')
k_epr_rate <- mixed(rate ~ condition2_c + gender_c +
                      (1 + condition2_c|speaker) +
                      (1 + condition2_c|item),
                    data = brown2014_z, method = 'LRT')
```

## Plot comparing Korean and Japanese across tasks and acoustic variables

First, let's create a vector of names for the models.

```{r model_names}
mypreds <- c('f0', 'f0sd', 'int', 'intsd', 'jit',
             'shim', 'h1h2', 'HNR', 'rate')
```

Set plotting parameters. x_fac determines the distance between the languages on the x-axis.

```{r plot_parts}
x_fac <- 0.2
```

The following is the actual plot. quartz() only works on Macs.

```{r big_plot}
quartz('', 12.5, 6)
par(mai = rep(0.1, 4), mfrow = c(2, 1),
    omi = c(0.75, 1.5, 0.25, 0.25))

# Plot 1:
plot(1, 1, type = 'n',
     xaxt = 'n', yaxt = 'n',
     xlab = '', ylab = '',
     xlim = c(0.5, length(mypreds) * 2 - 0.5),
     ylim = c(-1, 1))
abline(h = 0, lwd = 1.5, lty = 2)
axis(side = 2, at = seq(-1, 2, 0.5),
     las = 2, lwd.ticks = 2, font = 2, cex.axis = 1.05)
text(labels = 'Deferential - Nondeferential difference', x = -2.25, y = -1.25,
     font = 2, cex = 1.5, xpd = NA, srt = 90)
text(labels = '(z-scores)', 
     x = -1.7, y = -1.25,
     font = 2, cex = 1.25, xpd = NA, srt = 90)

# Plot 1, data:
for (i in seq_along(mypreds)) {
  jap_ppt <- summary(get(str_c('j_ppt_', mypreds[i])))
  jap_ppt <- jap_ppt$coefficients['condition2_c', ]
  
  kor_ppt <- summary(get(str_c('k_ppt_', mypreds[i])))
  kor_ppt <- kor_ppt$coefficients['condition2_c', ]
  
	# Korean:

	segments(x0 = seq(1, 18, 2)[i] - x_fac,
	         y0 = kor_ppt[1] - 1.96 * kor_ppt[2],
	         y1 = kor_ppt[1] + 1.96 * kor_ppt[2],
	         lwd = 2, col = 'grey55')

	points(x = seq(1, 18, 2)[i] - x_fac,
	       y = kor_ppt[1], pch = 21, cex = 1.15,
	       col = 'black', lwd = 2, bg = 'white')

	## Japanese:

	segments(x0 = seq(1, 18, 2)[i] + x_fac,
	         y0 = jap_ppt[1] - 1.96 * jap_ppt[2],
	         y1 = jap_ppt[1] + 1.96 * jap_ppt[2],
	         lwd = 2)
	
	points(x = seq(1, 18, 2)[i] + x_fac,
	       y = jap_ppt[1], pch = 15, cex = 1.15)

	}
 legend('topright',
        legend = c('Japanese', 'Korean'),
        pch = c(15, 21), col = 'black',
        pt.bg = c('black', 'white'), lwd = 2,
        cex = 1.1, box.lwd = 2)
  
text(x = 0.38, y = 0.85, labels = '(a)',
     font = 2, cex = 1.25)
mtext('Discourse Completion Task',
      line = -2, xpd = NA, font = 2, cex = 1.6)
box(lwd = 2)

# Plot 2:
plot(1, 1, type = 'n', xaxt = 'n', yaxt = 'n',
     xlab = '', ylab = '',
     xlim = c(0.5, length(mypreds) * 2 - 0.5),
     ylim = c(-1, 1))
abline(h = 0, lwd = 1.5, lty = 2)
axis(side = 2, at = seq(-1, 2, 0.5),
     las = 2, lwd.ticks = 2, font = 2, cex.axis = 1.15)
# Plot 2, data:
for (i in seq_along(mypreds)) {
	jap_epr <- summary(get(str_c('j_epr_', mypreds[i])))
	jap_epr <- jap_epr$coefficients['condition2_c', ]

	kor_epr <- summary(get(str_c('k_epr_', mypreds[i])))
	kor_epr <- kor_epr$coefficients['condition2_c', ]

	# Korean:

	segments(x0 = seq(1, 19, 2)[i] - x_fac,
	         y0 = kor_epr[1] - 1.96 * kor_epr[2],
	         y1 = kor_epr[1] + 1.96 * kor_epr[2],
	         lwd = 2, col = 'grey55')

	points(x = seq(1, 18, 2)[i] - x_fac,
	       y = kor_epr[1], pch = 21, cex = 1.15,
	       col = 'black', lwd = 2, bg = 'white')

	## Japanese:

	segments(x0 = seq(1, 19, 2)[i] + x_fac,
	         y0 = jap_epr[1] - 1.96 * jap_epr[2],
	         y1 = jap_epr[1] + 1.96 * jap_epr[2],
	         lwd = 2)
	
	points(x = seq(1, 18, 2)[i] + x_fac,
	       y = jap_epr[1], pch = 15, cex = 1.15)

	}
mtext('Reading Task', line = -2,
      xpd = NA, font = 2, cex = 1.6)
text(x = 0.38, y = 0.85,
     labels = '(b)', font = 2, cex = 1.25)
axis(side = 1, at = seq(1, 18, 2),
     font = 2, cex.axis = 1.10,
     labels = c('Pitch', 'Pitch SD', 'Intensity',
                'Intensity SD', 'Jitter', 'Shimmer', 
                'H1-H2', 'HNR', 'Rate'),
     lwd = 2, lwd.ticks = 2)
legend('topright',
       legend = c('Japanese', 'Korean'),
       pch = c(15, 21), col = 'black',
       pt.bg = c('black', 'white'), lwd = 2,
       cex = 1.1, box.lwd = 2)
box(lwd = 2)
quartz.save('../figures/production_comparison.png',
            dpi = 300)
quartz.save('../figures/production_comparison.tiff',
            dpi = 300)
```








